\renewcommand{\DictionaryHeadwordFormat}[1]{\textbf{#1}}


\section{A}

\section{I/E}

\entry{í\ppa ạyạ}[i\toneH p\jekt a\toneL ja\toneL]{n.coll.}[\ppt\Sgv{yo\ppa\ppa ạyạ}]{almond flour}[iphaya_HLL]
\begin{senses}
    \sense*{Almond flour or almond meal; the powder resulting from grinding almonds}
\end{senses}

\etym{iamb., underlyingly \enl{\suph{}í\ppa{}ạya}, from Old Elv. \lex{hiipopaa} + \lex{hi7aa}}


\entry{ẹn}{v.}{there is}[en_L]
\begin{senses}
    \sense*{there is, to exist, existential particle}
\end{senses}
\etym{troch., from Old Elv. \lex{7iina}}

\entry{ẹnị}{prt.}{there is not}[eni_LL]
\begin{senses}
    \sense*{there is not, existential negation particle}
\end{senses}
\etym{from Old Elv. \lex{7iina} + \lex{-7iiho}}

\entry{énłạlen}[ẽ\engma\toneH\vell a\toneL lẽn\toneM]{n.coll.}{En\l alen}[enLalen_HLM]
\begin{senses}
    \sense*{this language, En\l alen}
\end{senses}
\etym{troch., from Old Elv. \lex{hiina7alaa} + \lex{hiilino}}

\entry{ílyon}[il\toneH jũn\toneM]{n.}{utterance}[ilyon_HM]
\begin{senses}
    \sense*{an utterance, statement, or sentence}
\end{senses}
\etym{dacty., from Old Elv. \lex{hiilino}}
\begin{enumerate}
    \item[] \entry{ẹn ílyon}{v.phras.}{to be sapient}[en_L ilyon_HM]
    \begin{senses}
        \sense{to be capable of speaking, to know how to talk, to possess language}
        \sense{to be sapient, to be intelligent, to be mentally aware, to have one's faculties}
    \end{senses}
\end{enumerate}

\section{O}

\entry{ófị}{prt.}{not (\Ipfv)}[ofi_HL]
\begin{senses}
    \sense*{imperfective negation particle}
\end{senses}
\etym{from Old Elv. \lex{hoofi} + \lex{-7iiho}}

\section{R}

\section{Y}

\section{W}

\section{P}

\entry{pol}{num.}{two}[pol_M]
\begin{senses}
    \sense*{two}
\end{senses}
\etym{troch., from Old Elv. \lex{poola}}

\section{T}

\entry{tóyó}{prt.}{not (\Pfv)}[toyo_HH]
\begin{senses}
    \sense*{perfective negation particle}
\end{senses}
\etym{from Old Elv. \lex{too} + \lex{-7iiho}}

\section{K}

\section{\Ppa}

\section{\Tta}

\entry{\tta ẹmo}{n.coll.}{eyes}[themo_LM]
\begin{senses}
    \sense*{eyes}
\end{senses}
\etym{iamb., from Old Elv. \lex{to7iimomoo}}

\section{\Kka}

\section{F}

\section{S}

\entry{séngạ}{num.}{three}[senga_HL]
\begin{senses}
    \sense*{three}
\end{senses}
\etym{iamb., from Old Elv. \lex{siini7aa}}

\section{M}

\entry{matí}{n.}{elf}[mati_MH]
\begin{senses}
    \sense*{elf, person, an individual who is an elf}
\end{senses}
\etym{dacty., underlyingly \enl{matí\suphi{}}, from Old Elv. \lex{pamaati7i}}

\section{N}

\section{\Engga}

\section{L}

\section{Ł}
